2040 greenhouse gas reduction targets and energy transitions in line with the EU Green Deal

### 2025-05-06 report_additionalCharts.Rmd
general update for charts

nonAchieved2030 <- left_join(
  df %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
    group_by(tgt2030) %>% 
    mutate(min = min(value),
           max = max(value)),
  df %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
    mutate(price_2030 = currencyConversion*value) %>%
    select(scenario, price_2030),
  by = "scenario") %>%
  filter(diff >= 0.5 | diff <= -0.5) %>%
  select(scenario, price_2030, tgt2030, tgtAchieved, diff) %>%
  arrange(desc(abs(diff)))

>>>>

nonAchieved2030 <- left_join(
  df %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
    group_by(tgt2030) %>% 
    mutate(min = min(value),
           max = max(value)),
  df %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
    mutate(price_2030 = currencyConversion*value) %>%
    select(scenario, price_2030),
  by = "scenario")

underAchieved2030 <- nonAchieved2030 %>%
  filter(diff >= 0.5) %>%
  select(scenario, price_2030, tgt2030, tgtAchieved, diff) %>%
  arrange(desc(abs(diff)))

overAchieved2030 <- nonAchieved2030 %>%
  filter(diff <= 0.5) %>%
  select(scenario, price_2030, tgt2030, tgtAchieved, diff) %>%
  arrange(desc(abs(diff)))

rerun <- overAchieved2030 %>% filter(tgtAchieved >= 59.5)

### 2025-05-06 report_paperCharts.Rmd
general update for charts

@@

# Industry Emissions
vars <- c("Chemicals"="Emi|CO2|Energy|Demand|Industry|Chemicals",
          "Other Industry"="Emi|CO2|Energy|Demand|Industry|Other Industry",
          "Steel"="Emi|CO2|Energy|Demand|Industry|Steel",
          "Cement" = "Emi|CO2|Energy|Demand|Industry|Cement"
          )

plotColor <- c(
  "Cement" = "#355070",
  "Steel" = "#219ebc",
  "Chemicals" = "#eaac8b",
  "Other Industry" = "#e56b6f"
)

@@

plotData <- df %>%
  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
  mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
         value = currencyConversion*value,
         tgt2030 = factor(tgt2030, levels=c(55,57,59)),
         efficiency = factor(efficiency, levels=c("reference", "EED 2018 Eff", "FitFor55 eff", "RePowerEU eff")),
         bioLim = factor(bioLim, levels=c("BioLim4", "BioLim7.5", "BioLim12", "BioLim20")),
         lim = factor(lim, levels=c("default", "limCCS", "limH2", "limVRE"))
         )

@@

g[["Carbon Price - line"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
  geom_line(size = 0.5, aes(linetype=tgt2030, color = efficiency)) +
  geom_point(size = 3, aes(shape = lim, fill = bioLim)) +
  geom_line(data=ETS_price,aes(x=Date, y=Price),size=0.5, color = "#000000") +
  geom_label_repel(data=ETS_price %>% filter(Date == "2008-09-19"), aes(x=Date, y=Price, label = variable),
                     #label = "ETS Price",
                     nudge_x = 0,
                     nudge_y = 250,
                     segment.square = TRUE,
                     point.padding = 0,
                     hjust = 0,
                     direction="y",
                     size = geomText.size*0.8) +
  scale_x_date(date_labels = "%Y") +
  scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1))) +   
  scale_color_manual(values = c("reference"="#ae0000", "EED 2018 Eff"="#db4646", "FitFor55 eff"="#0090ab", "RePowerEU eff"="#095786"), guide = guide_legend(nrow =2, byrow = F, order = 2, override.aes = list(linewidth = 1.5))) + 
  scale_fill_manual(values = c("BioLim4"="#fedc97", "BioLim7.5"="#b5b682", "BioLim12"="#7c9885", "BioLim20"="#28666e"), guide = guide_legend(nrow =2, byrow = F, override.aes = list(shape = 21, size = 6, colour = "transparent"), order = 3)) +
  scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 6))) +
  labs(title = expression(paste("(a) Carbon price (€/t ", CO[2],")"))) +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank(),
        strip.text.y = element_blank(),
        legend.key.width = unit(2,"cm"),
        legend.position="right", 
        legend.direction = "vertical", 
        legend.box = "vertical",
        legend.spacing.y = unit(0.2, "lines"))

@@

 ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 5. EU-27 Electricity generation.svg"), g[["Supplementary figure 5"]] , device="svg", width = 12, height = 10, dpi=100, units = "in")
 ggsave(paste0(outChartsFolder,"/png/Supplementary figure 5. EU-27 Electricity generation.png"), g[["Supplementary figure 5"]] , device="png", width = 12, height = 10, dpi=300, units = "in")

>>>>

steel_df %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

# Industry Emissions
vars <- c("Other Industry"="Emi|CO2|Energy|Demand|Industry|Other Industry",
          "Chemicals - Energy"="Emi|CO2|Energy|Demand|Industry|Chemicals",
          #"Chemicals - Feedstock"="Emi|CO2|Industrial Processes|Chemicals", 
          "Steel"="Emi|CO2|Energy|Demand|Industry|Steel",
          "Cement" = "Emi|CO2|Energy|Demand|Industry|Cement"
          )

plotColor <- c(
  "Cement" = "#355070",
  "Steel" = "#219ebc",
  "Chemicals - Energy" = "#eaac8b",
  "Chemicals - Feedstock" = "#e56b6f",
  "Other Industry" = "#b59765"
)

@@

labels <- c(
  "55"="55%",
  "57"="57%",
  "59"="59%",
  "reference"="reference", 
  "EED 2018 Eff"="EED 2018", 
  "FitFor55 eff"="FitFor55", 
  "RePowerEU eff"="RePowerEU",
  "BioLim4"="4 EJ",
  "BioLim7.5"="7.5 EJ", 
  "BioLim12"="12 EJ", 
  "BioLim20"="20 EJ",
  "default"="default",
  "limCCS"="limited CCS",
  "limH2"="limited H2",
  "limVRE"="limited VRE"
)

plotData <- df %>%
  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
  mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
         value = currencyConversion*value,
         tgt2030 = labels[as.character(tgt2030)],
         efficiency = labels[as.character(efficiency)],
         bioLim = labels[as.character(bioLim)],
         lim =  labels[as.character(lim)]
  ) %>%
  mutate(tgt2030 = factor(tgt2030, levels=labels[c("55","57","59")]),
         efficiency = factor(efficiency, levels=labels[c("reference", "EED 2018 Eff", "FitFor55 eff", "RePowerEU eff")]),
         bioLim = factor(bioLim, levels=labels[c("BioLim4", "BioLim7.5", "BioLim12", "BioLim20")]),
         lim = factor(lim, levels=labels[c("default", "limCCS", "limH2", "limVRE")])
         )

@@

g[["Carbon Price - line"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
  geom_line(size = 0.5, aes(linetype=tgt2030, color = efficiency)) +
  geom_point(size = 3, aes(shape = lim, fill = bioLim)) +
  geom_line(data=ETS_price,aes(x=Date, y=Price),size=0.5, color = "#000000") +
  geom_line(data=plotData %>% filter(scenario == mainScen), size = 1.5, color = "black") +
  geom_label_repel(data=ETS_price %>% filter(Date == "2008-09-19"), aes(x=Date, y=Price, label = variable),
                     #label = "ETS Price",
                     nudge_x = 0,
                     nudge_y = 250,
                     segment.square = TRUE,
                     point.padding = 0,
                     hjust = 0,
                     direction="y",
                     size = geomText.size*0.8) +
  scale_x_date(date_labels = "%Y") +
  geom_label_repel(data = data.frame(period=as.Date("02/07/2037",format="%m/%d/%Y"), value= plotData %>% filter(scenario == mainScen) %>% filter(period == "2035-01-01" | period == "2040-01-01") %>% pull(value) %>% sum() / 2, scenario=mainScen), aes(x=period,y=value),
                     label = "Reference scenario",
                     nudge_x = 0,
                     nudge_y = 550,
                     segment.square = TRUE,
                     point.padding = 0,
                     hjust = 1,
                     direction="y",
                     size = geomText.size*0.8) +
  scale_x_date(date_labels = "%Y") +
  scale_linetype_manual(values = c("55%"="twodash", "57%"="solid", "59%"="dashed"), guide = guide_legend(title="Short-term policy", nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1))) +   
  scale_color_manual(values = c("reference"="#ae0000", "EED 2018"="#db4646", "FitFor55"="#0090ab", "RePowerEU"="#095786"), guide = guide_legend(title="Efficiency target", nrow =2, byrow = F, order = 2, override.aes = list(linewidth = 1.5))) + 
  scale_fill_manual(values = c("4 EJ"="#fedc97", "7.5 EJ"="#b5b682", "12 EJ"="#7c9885", "20 EJ"="#28666e"), guide = guide_legend(title="Biomass availability limited to", nrow =2, byrow = F, override.aes = list(shape = 21, size = 6, colour = "transparent"), order = 3)) +
  scale_shape_manual(values = c("default"=21,"limited CCS"=22,"limited H2"=23,"limited VRE"=24), guide = guide_legend(title="Technology evolution", nrow =2, byrow = T, order = 4, override.aes = list(size = 6))) +
  labs(title = expression(paste("(a) Carbon price (€/t ", CO[2],")"))) +
  theme_doubleColumn_alt() +
  theme(axis.title.y=element_blank(),
        strip.text.y = element_blank(),
        legend.key.width = unit(1.5,"cm"),
        legend.position="right", 
        legend.direction = "vertical", 
        legend.box = "vertical",
        legend.spacing.y = unit(0.2, "lines"),
        legend.title=element_text(size=text_size*0.8)#,
        #legend.text=element_text(size=2*geomText.size)
        ) +
  scale_y_continuous(breaks = seq(0, 1200, by = 300)) +
  expand_limits(y=1200)

@@

 ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 5. EU-27 Electricity generation.svg"), g[["Supplementary figure 5"]] , device="svg", width = 12, height = 9, dpi=100, units = "in")
 ggsave(paste0(outChartsFolder,"/png/Supplementary figure 5. EU-27 Electricity generation.png"), g[["Supplementary figure 5"]] , device="png", width = 12, height = 9, dpi=300, units = "in")
